Efficient and Effective Metric Space Indexing for Complete Record Linkage

### 2017-11-20 paper.tex
Update on Overleaf.

We explore the efficacy of several similarity search algorithms for
record linkage: traditional blocking, one popular incomplete algorithm, LSH-minhash, and one complete
method, M-tree~\cite{paolociaccia2m}. We also use a simple brute force
(nested-loop) exact technique as a baseline for comparison, although
this approach can only feasibly be applied to the smallest of our
datasets. All experiments have a number of parameters with which we can
configure the search space and algorithm behaviour, as described in
Sect.~\ref{sec-exp}. A \emph{distance threshold}, $d$, specifies a
maximum distance, equivalent to a minimum similarity, for two records to
be classified as a link (i.e.\ referring to the same entity).

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Number of~ & ~Number of true~ & ~Linkage~ & ~Entities\\
  name(s)  & records  & matching pairs & type & linked \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 17,184 & many-many & publication-publication\\
  NCVR  & ~448,134~ & ~148,036~ & 1:1  & voter-voter\\
  Isle of Skye & 32,567 & 2,900 & 1:1 & birth-death\\
  Kilmarnock  & 70,852 & 8,300 & 1:1 & birth-death\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

\smallskip
\textbf{Data Sets:}
%\label{sec-data}
We used four real data sets from three domains in our experiments as
summarized in Table~\ref{table-datasets}. The first is
\emph{CORA}~\footnote{Available from:
\texttt{http://secondstring.sourceforge.net}}, which contains 1,295
records that refer to 112 machine learning publications. Ground truth is provided via a unique
\emph{paper\_id} identifier of the form "blum1993".

The second are two snapshots of the North Carolina Voter Registration
database (\emph{NCVR})~\footnote{Available from: \texttt{http://dl.ncsbe.gov/}}, which were collected in April and June
2014. Each of these contains records of voters and includes their
first names, surnames, and addresses. Ground truth is provided via a
\emph{NCID} identifier which uniquely identifies a voter. In our
experiments we use two randomly selected sub-sets of $224,073$ and
$224,061$ records, respectively, where $148,036$ of those refer to
voters that occurred in both original NCVR snapshots but had name
and/or address changes over time (thus leading to around $66\%$
matching records).

@@

%The experiments for each technique have been run within a generic Java framework which permits the actual linkage method used to be supplied. This ensures that the algorithms are consistently executed and that true comparisons of the their behaviour can be reported. It supplies each algorithm with the source records to be matched using an \emph{addSourceRecord} method which takes a record as a parameter. For each of the records to be matched a  \emph{getCandidateMatches} method is called which is expected to return a list of the linked records from the sources. Each of our datasets contains ground truth with which we can establish the records that are true links and those that are not (discussed below). From this ground truth the framework can report the number of links make, linkage quality etc.

FFFXXXTTT
We we will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.

@@

\begin{table}[t]
\caption{Parameter settings used for the different data sets used in
   the experiments,with $d$ the distance threshold used, $t_b$ the
   M-tree branching factor, $l_{ss}$, $l_{sb}$ and $l_{nb}$ the LSH
   shingle size, and the size and number of bands, respectively.}
 \label{table-parameters}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{cccccccc}
  \hline\noalign{\smallskip}
  Data set~ & $d$ & $t_b$ & $l_{ss}$ & $l_{bs}$ & $l_{nb}$ & 
    $f_{ki}$ & $f_{ks}$ \\
  name(s) & & & & & & & \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA & ~$[0,5,10,\ldots,95,100]$~ & ~$[5,10,25,50]$~ & ~$2$~ &
    ~$[2,5,10]$~ & ~$[2,5,10]$~ & ~$[30,35,40]$~ & ~$[30,35,40]$ \\
  NCVR  &  \\
  Isle of Skye &  \\
  Kilmarnock  &  \\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

\smallskip
\textbf{Experimental Setup:}
%
We implemented all techniques described in Sect.~\ref{sec-approach}
using Java (version 1.8.0\_144) and ran an extensive et of experiments on
a compute server with 24 Intel(R) Xeon(R) CPU E5-2630 processors running at 2.30GHz, 
128 GBytes of main memory and running Red Hat 4.8.5-11.

@@

>>>>

The general problem we address is that for two datasets A and B, we wish
to find all the records from dataset B that match each record from dataset A.
We explore the efficacy of several similarity search algorithms for
record linkage: traditional blocking, one popular incomplete algorithm, LSH-minhash, and one complete
method, M-tree~\cite{paolociaccia2m}. We also use a simple brute force
(nested-loop) exact technique as a baseline for comparison, although
this approach can only feasibly be applied to the smallest of our
datasets. All experiments have a number of parameters with which we can
configure the search space and algorithm behaviour, as described in
Sect.~\ref{sec-exp}. A \emph{distance threshold}, $d$, specifies a
maximum distance, equivalent to a minimum similarity, for two records to
be classified as a link (i.e.\ referring to the same entity).

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Records in~& ~Records in~ & ~Number of true~& ~Entities\\
  name(s)  & dataset1  & dataset2  & matching pairs & linked \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 1295 & 17,184 & publication-publication\\
  NCVR  & ~224,073~ & 224,061 & ~148,036~ & voter-voter\\
  Isle of Skye & 17,612 & 12,284& 2,900 & birth-death\\
  Kilmarnock  & 38,430 & 23,714 & 8,300 & birth-death\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

\smallskip
\textbf{Data Sets:}
%\label{sec-data}
We used four real data sets from three domains in our experiments as
summarized in Table~\ref{table-datasets}. The first is
\emph{CORA}~\footnote{Available from:
\texttt{http://secondstring.sourceforge.net}}, which contains 1,295
records that refer to 112 machine learning publications. Ground truth is provided via a unique
\emph{paper\_id} identifier of the form "blum1993". In this experiment linkage is performed over the same set of records.

The second are two randomly selected sub-sets extracted from the North Carolina Voter Registration
database (\emph{NCVR})~\footnote{Available from: \texttt{http://dl.ncsbe.gov/}}, which were collected in April and June
2014. Each of these contains records of voters and includes their
first names, surnames, and addresses. Ground truth is provided via a
\emph{NCID} identifier which uniquely identifies a voter.

@@

@@

\begin{table}[t]
\caption{Parameter settings used for the different data sets used in
   the experiments,with $d$ the distance threshold used, $l_{ss}$, $l_{sb}$ and $l_{nb}$ the LSH
   shingle size, and the size and number of bands, respectively.}
 \label{table-parameters}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{ccccc}
  \hline\noalign{\smallskip}
  Data set~ & $d$ & $l_{ss}$ & $l_{bs}$ & $l_{nb}$ \\
  name(s) & & & &  \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA & ~$[0,5,10,\ldots,95,100]$~ & ~$2$~ &
    ~$[2,5,10]$~ & ~$[2,5,10]$~  \\
  NCVR  &  \\
  Isle of Skye &  \\
  Kilmarnock  &  \\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

\smallskip
\textbf{Experimental Setup:}
%
We implemented all techniques described in Sect.~\ref{sec-approach}
using Java (version 1.8.0\_144) and ran an extensive set of experiments on
a compute server with 24 Intel(R) Xeon(R) processors running at 2.30GHz, 
128 GBytes of main memory and running Red Hat 4.8.5-11.

@@

%the following is a sentence we culled earlier but may be needed.
We we will evaluate the performance of LSH based blocking with regard to the three parameters $l_{ss}$, $l_{bs}$ and $l_{nb}$ in
Sect.~\ref{sec-exp}.
